Practical Optional Types for Clojure

### 2015-02-25 overview.tex
add circleci example

Typed Clojure knows that this \clj{merge} will preserve the entries
of the left hand map.

\begin{Code}
\begin{exmp}
\inputminted[firstline=25,lastline=25]{clojure}{code/demo/src/demo/hmap_path.clj}
\end{exmp}
\end{Code}

@@

\begin{minted}{clojure}
(ann rep [Any -> String])
(defmulti rep class)
(defmethod rep Number [x] (str (inc x)))
(defmethod rep Keyword [x] (str (name x)))

(rep :a) ;=> "a"
(rep 1)  ;=> "2"
\end{minted}

@@

\inputminted[firstline=4,lastline=23]{clojure}{code/demo/src/demo/eg5.clj}

@@

\inputminted[firstline=6,lastline=23]{clojure}{code/demo/src/demo/eg7.clj}

@@

\inputminted[firstline=6,lastline=20]{clojure}{code/demo/src/demo/eg8.clj}

>>>>

The next example is a real Typed Clojure program written by CircleCI, who maintain a large production
installation of Clojure (see section~\ref{sec:casestudy} for a case study).

\begin{Code}
\begin{exmp}
\inputminted[firstline=10,lastline=22]{clojure}{code/demo/src/demo/key.clj}
\end{exmp}
\end{Code}

\clj{enc-keypair} takes an unencrypted keypair and returns an encrypted keypair by
removing the raw private key and attaching an encrypted private key.
Since \clj{EncKeyPair} is \clj{:complete?}, Typed Clojure enforces the return type
does not contain an entry \clj{:private-key}, and would complain if the \clj{dissoc}
operation forgot to remove it.

@@

\begin{Code}
\begin{exmp}
\begin{minted}{clojure}
(ann rep [Any -> String])
(defmulti rep class)
(defmethod rep Number [x] (str (inc x)))
(defmethod rep Keyword [x] (str (name x)))

(rep :a) ;=> "a"
(rep 1)  ;=> "2"
\end{minted}
\end{exmp}
\end{Code}

@@

\begin{Code}
\begin{exmp}
\inputminted[firstline=4,lastline=23]{clojure}{code/demo/src/demo/eg5.clj}
\end{exmp}
\end{Code}

@@

\begin{Code}
\begin{exmp}
\inputminted[firstline=6,lastline=23]{clojure}{code/demo/src/demo/eg7.clj}
\end{exmp}
\end{Code}

@@

\begin{Code}
\begin{exmp}
\inputminted[firstline=6,lastline=20]{clojure}{code/demo/src/demo/eg8.clj}
\end{exmp}
\end{Code}
